---
title: "Section example"
author: "David Kaiser; david.kaiser.82@gmail.com"
output:
  html_document:
    df_print: paged
---

Function to draw a section of interpolated data along a transect

 + accepts vectors of corresponding lon, lat, depth, and data values
 + accepts the input of bathymetry data as class "bathy", or creates bathymetry
 + requires selection of distance, longitude or latitude as x values
 + requires selection of a dominant section orientation towards N, E, S or W
 + requires the following packages to be installed: "sp", "marmap", "reshape2", "MBA", and "ggplot2"
 + value is a list containing a ggplot of the sections with interpolated data and bathymetry profile and three data frames containing the interpolated data, the bathymetry profile, and the input data with section distance [km] added, respectively.
  The list objects are named "plot", "output", "profile", and "input", respectively.

```{r}
source("section_DK.R")
```

```{r}
example.results <- section.DK(longitude = 15:20,
                              latitude = 50:55,
                              parameter = 13:18,
                              depth = 0:5)

example.results$plot

head(example.results$input)

head(example.results$output)

head(example.results$profile)

```

## ToDo:

 + labeled contour lines (not provided by ggplot geom_contour function, available workaround 'directlabels' does not help)