---
title: "Section"
author: "David"
output: github_document
---

```{r setup, include=FALSE}
source("section_DK.R")
```

### Description

A function to draw an oceanographic section of interpolated data along a transect. Requires packages `sp`, `marmap`, `MBA`, `reshape2`, and `ggplot2`.

### Arguments

  *longitude* -- vector of latitude in degrees north
  
  *latitude* -- vector of longitude in degrees east
  
  *parameter* -- vector of values of parameter z to be interpolated and plotted as color; accepts NAs but all Lon-Lat-Depth-Parameter combinations with parameters NA will be removed
  
  *depth* -- vector of depth values in m, negative numbers are accepted but will be converted to positives
  
  *xy.ratio* = NULL -- optional integer vector of length 2 in which first and second integers indicate the relative strength of interpolation in x and y direction, defaults to NULL and calculates the required values according to mean depth resolution and distance between stations
  
  *section.x* = "km" -- unit for x axis of the section; options are "km" (the default), "degE", and "degN"
  
  *section.direction* = NA -- optional sorting of data by stations along a dominant direction. Options are "N", "E", "S", and "W", e.g. "S" creates a section running from north to south. If nothing is input, data vectors will not be resorted
  
  *bathymetry* = NULL -- optional bathymetry of class "bathy", if not supplied will be retrieved from NOAA for the domain of "longitude" and "latitude"
  
  *keep.bathy* = FALSE -- should the downloaded bathymetry be kept offline; this would make repeated plotting faster
  
  *max.depth* = "profile" -- select the section's maximum depth in bathymetry ("profile", the default) or in data ("data") as the maximum depth of the plot
  
  *contour.breaks* = 5 -- either an integer defining the number of contour bins (defaults arbitrarily to 5), or a vector of values for the contour lines. 

### Value

A named list containing the \$plot, the \$input data with the distance of stations along the section (according to sorting via *section.direction*), the \$output data of the interpolated results (as a long table), and the \$profile of bathymetry under the section.

### Example

The example data from the Black Sea is available for download [from PANGEA](https://doi.pangaea.de/10.1594/PANGAEA.898717). 
Because the downloaded data is not sorted properly, the general cruise direction from west to east is indicated by *section.direction = "E"*.
```{r example, message=FALSE}
data <- read.table("Kaiser-etal_MSM33.tab", sep = "\t", skip = 99, header = TRUE)

example <- section(longitude = data$Longitude,
                   latitude = data$Latitude,
                   parameter = data$Sal,
                   depth = data$Depth.water..m.,
                   section.direction = "E")
```

### Output

#### Plot

```{r plot, warning=FALSE, message=FALSE}
example$plot 
```

Because the \$plot is a ggplot2 object, it can be modified and extended.
```{r plot_extra, warning=FALSE, message=FALSE}
example$plot +
  coord_cartesian(ylim=c(500,0)) +
  metR::geom_label_contour(data = example$output,
                           aes(section.x, depth, z = parameter)) +
  scale_fill_gradientn(colours = c("black", "grey", "white"), name = "salinity")
```

#### Tables
The other objects in the results list are simple data frames.
```{r tables}
head(example$input)

head(example$output)

head(example$profile)
```
